Compare pseqs

### 2019-10-17 comparepseqs.Rmd
Duplicated line
Atlas changes

covariates.min <- c("BL_AGE", "SEX")
covariates.full <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE",
                         "Q57X", "BL_USE_RX_C03", "BL_USE_RX_C07",
                         "BL_USE_RX_C08", "BL_USE_RX_C09")
```

@@

```{R models}
mclapply(c2l(names(rds)), function(key) {
    pseq.species <- import_filter_data(rds[[key]],
                               included = c("MEN", "BL_AGE", "SYSTM", "DIASM", "BMI",
                                            "CURR_SMOKE", "BL_USE_RX_C09",
                                            "Q57X", "BL_USE_RX_C03",
                                            "BL_USE_RX_C07", "BL_USE_RX_C08"))

@@

    g4 <- plot.diversities(diversities)
    ggsave(file = sprintf("cache/comparepseqs-%s.png", key), plot=g4, height=6, width=9)
}, mc.cores = length(rds))
```

>>>>

var.CL.min <- c("BL_AGE", "SEX")
var.CL <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", 
            "BL_USE_RX_C03","BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09")
```

@@

```{R models}
plots <- mclapply(c2l(names(rds)), function(key) {
    pseq.species <- import_filter_data(rds[[key]],
                               included = c("MEN", "BL_AGE", "SYSTM", "DIASM", "BMI",
                                            "CURR_SMOKE", "BL_USE_RX_C09",
                                            "Q57X", "BL_USE_RX_C03",
                                            "BL_USE_RX_C07", "BL_USE_RX_C08"))

@@

    g4 <- plot.diversities(diversities)
    ggsave(file = sprintf("cache/comparepseqs-%s.png", key), plot=g4, height=6, width=9)
	g4
}, mc.cores = length(rds))
```

```{r save session}
save.image(file = "session/comparepseq.Rdata")
```
